---
title: "Summarize the R Configuration intended for Southwick Use"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
output: 
    html_document:
        toc: true
        toc_float: true
        code_folding: hide
---

```{r setup, message=FALSE}
library(tidyverse)
knitr::opts_chunk$set(comment = NA)
```

## Overview

There are 3 basic customizations performed by the Southwick R Installation:

- Creates an *Renviron.site* to specify a user library
- Creates an *Rprofile.site* to specify a CRAN repo
- Installs some commonly used packages (built by Southwick and otherwise)

## Details

If you want to dig into the details, take a look below.

### Renviron.site

See `?startup` for background about Renviron and Rprofile. The Renviron customization serves 2 purposes:

- specifies a user library, protecting the System Library from accidental installations
- defines other useful environmental variables (e.g., Census API key)

```{r}
file.path(R.home(component = "etc"), "Renviron.site") %>%
    readLines()
```

### Rprofile.site

The Rprofile customization serves 3 purposes:

- sets the default CRAN repo, to ensure package installs come from the same MRAN snapshot
- create a user library if it doesn't exist, to ensure System Library is protected from installs
- prints a startup message, to inform the user of the Southwick-specific R installation

```{r}
file.path(R.home(component = "etc"), "Rprofile.site") %>%
    readLines()
```

### Packages Installed to System Library

Quite a few of these installed packages come from "02-install-site-library.R"

```{r}
r_install <- read.csv("pkg/installed-base-pkgs.csv")
new_install <- installed.packages() %>%
    data.frame() %>%
    select(Package, Version) %>%
    mutate(install_source = "Southwick-Install")
install <- bind_rows(r_install, new_install)
write.csv(install, file = "pkg/installed-pkgs.csv")
DT::datatable(install)
```

```{r}
sessionInfo()
```
